Verifying Demonstrations

### 2017-09-30 protocol.tex
Adds a third required property for storage

There are exactly two properties that we need.
The first property we need is decentralized, immutable storage with a general 
form of time-stamping.
I.e.\ once we commit something to the blockchain it will remain there and we do 
not have to trust any central authority.
We can also relate commitments to time, e.g.\ in Bitcoin~\cite{Bitcoin} a new 
block appears approximately every 10 minutes.

@@

>>>>

There are three properties that we need from the storage system.
The first property we need is decentralized, immutable storage with a general 
form of time-stamping.
I.e.\ once we commit something to the blockchain it will remain there and we do 
not have to trust any central authority.
We can also relate commitments to time, e.g.\ in Bitcoin~\cite{Bitcoin} a new 
block appears approximately every 10 minutes.

@@

The third property is that once we have committed some data, we do not need to 
keep the data itself, but we can store some confirmation value instead.
E.g.\ using blockchains, we can store the hash of the block where our data was 
committed, while this block remains we are sure that our data remains committed 
--- even if we no longer remember what our data looked like.
We will use this property to approximate the property of receipt freeness.
